Ovarian and prostate models

### 2020-11-09 src/s_hyperparameters.Rmd
cleaning up repo and rerunning rhat experiments

@@

# GBM
AR1 model
```{r}
f_ar1 <- function(rho, sigma, L){
  x <- vector(length = L)
  x[1] <- rnorm(1, 0, sd=sigma)
  for(i in 2:L)
    x[i] = rho * x[i - 1] + rnorm(1, 0, sd=sigma)
  return(x)
}

# Generates three chains with same var; one with a different var
f_generate_lower_var_four <- function(var_ratio, rho, sigma, L){
  x <- matrix(nrow = L, ncol = 4)
  for(i in 1:3)
    x[, i] <- f_ar1(rho, sigma, L)
  z <- f_ar1(rho, sigma * sqrt(var_ratio), L)
  x[, 4] <- z
  return(x)
}
```

```{r}
f_data_ar1 <- function(){
  temp <- f_generate_lower_var_four(1/3, 0.3, 1, 1000)
  a_array <- array(dim=c(1000, 4, 1))
  a_array[,,1] <- temp
  return(a_array)
}

f_replicate_hyper <- function(m_parameters, f_data_generator){

  a_array <- f_data_generator()

  laccuracy <- vector(length = nrow(m_parameters))
  for(i in 1:nrow(m_parameters))
    laccuracy[i] <- r_star(a_array,
                           caret_default=expand.grid(interaction.depth=m_parameters$int.depth[i],
                                                     n.trees = m_parameters$n.trees[i],
                                                     shrinkage=0.1,
                                                     n.minobsinnode=10))
  return(laccuracy)
}

f_replicate_r_star <- function(nreplicates, m_parameters, f_data_generator){
  r_star_vals <- matrix(nrow = nreplicates, ncol=nrow(m_parameters))
  for(i in 1:nreplicates){
      print(i)

    temp <- f_replicate_hyper(m_parameters, f_data_generator)
    r_star_vals[i, ] <- temp
  }
  r_star_vals <- r_star_vals %>% 
    t() %>% 
    as.data.frame()
  r_star_vals1 <- m_parameters %>% cbind(r_star_vals)
  return(r_star_vals1)
}

# m_parameters <- expand_grid(int.depth=seq(1, 7, 2),
#                             n.trees=c(1, 10, 50, 100))
# r_star_vals <- f_replicate_r_star(2, m_parameters, f_data_ar1)

# saveRDS(r_star_vals, "../data/ar1_sensitivity.rds")
g1 <- readRDS("../data/hypers_ar1.rds")$r_star %>% 
  melt(id.vars=c("int.depth", "n.trees")) %>% 
  group_by(int.depth, n.trees) %>% 
  summarise(lower=quantile(value, 0.25),
            middle=quantile(value, 0.5),
            upper=quantile(value, 0.75)) %>% 
  mutate(default=if_else(int.depth==3&n.trees==50, 1, 0)) %>% 
  ggplot(aes(x=as.factor(n.trees), y=middle, colour=as.factor(int.depth), group=as.factor(int.depth))) +
  geom_pointrange(aes(ymin=lower, ymax=upper, shape=as.factor(default)),
                  position=position_dodge2(width=0.1)) +
  geom_line(position=position_dodge2(width=0.1)) +
  xlab("# trees") +
  ylab("R*") +
  theme(text = element_text(size=16, colour="black"),
        axis.text = element_text(colour="black"),
        legend.position = c(0.7, 0.25)) +
  scale_y_continuous(limits=c(0.95, 1.3)) +
  geom_hline(yintercept = 1, linetype=2) +
  scale_color_brewer("Int. depth", palette = "Dark2") +
  guides(colour = guide_legend(nrow = 2, byrow = T)) +
  scale_shape(guide="none") +
  ggtitle("A. GBM")
```

8 schools
```{r}
# source("eight_schools.data.R")
# eight_schools <- list(J=J, y=y, sigma=sigma)
# model_cp <- stan_model("eight_schools_cp.stan")
# model_ncp <- stan_model("eight_schools_ncp.stan")
# 
# f_data_8_schools <- function(){
#   fit_ncp <- sampling(
#     model_ncp, data = eight_schools,
#     iter = 2000, chains = 4, refresh = 0,
#     control = list(adapt_delta = 0.95)
#     )
#   x_ncp <- rstan::extract(fit_ncp, permuted=F)
# }
# 
# m_parameters <- expand_grid(int.depth=c(1, 3, 5),
#                             n.trees=c(1, 50, 200))
# r_star_vals <- f_replicate_r_star(20, m_parameters, f_data_ar1)

g1a <- readRDS("../data/hypers_8_schools.rds")$r_star %>% 
  melt(id.vars=c("int.depth", "n.trees")) %>% 
  group_by(int.depth, n.trees) %>% 
  summarise(lower=quantile(value, 0.25),
            middle=quantile(value, 0.5),
            upper=quantile(value, 0.75)) %>% 
  mutate(default=if_else(int.depth==3&n.trees==50, 1, 0)) %>% 
  ggplot(aes(x=as.factor(n.trees), y=middle, colour=as.factor(int.depth), group=as.factor(int.depth))) +
  geom_pointrange(aes(ymin=lower, ymax=upper, shape=as.factor(default)),
                  position=position_dodge2(width=0.1)) +
  geom_line(position=position_dodge2(width=0.1)) +
  xlab("# trees") +
  ylab("R*") +
  theme(text = element_text(size=16, colour="black"),
        axis.text = element_text(colour="black"),
        legend.position = c(0.7, 0.7)) +
  scale_y_continuous(limits=c(0.95, 1.6)) +
  geom_hline(yintercept = 1, linetype=2) +
  scale_color_brewer("Int. depth", palette = "Dark2") +
  guides(colour = guide_legend(nrow = 2, byrow = T)) +
  scale_shape(guide="none") +
  ggtitle("A. GBM")
```

Cauchy
```{r}
f_data_cauchy <- function(){
  fit_nom <- stan(file = 'cauchy_alt_1.stan',
                refresh = 0)
  x <- rstan::extract(fit_nom, permuted=F)
  return(x)
}

# m_parameters <- expand_grid(int.depth=c(3, 7, 11),
#                             n.trees=c(50, 100, 400))
# r_star_vals <- f_replicate_r_star(2, m_parameters, f_data_cauchy)

g1b <- readRDS("../data/hypers_cauchy.rds")$r_star %>% 
  melt(id.vars=c("int.depth", "n.trees")) %>% 
  group_by(int.depth, n.trees) %>% 
  summarise(lower=quantile(value, 0.25),
            middle=quantile(value, 0.5),
            upper=quantile(value, 0.75)) %>% 
  mutate(default=if_else(int.depth==3&n.trees==50, 1, 0)) %>% 
  ggplot(aes(x=as.factor(n.trees), y=middle, colour=as.factor(int.depth), group=as.factor(int.depth))) +
  geom_pointrange(aes(ymin=lower, ymax=upper, shape=as.factor(default)),
                  position=position_dodge2(width=0.1)) +
  geom_line(position=position_dodge2(width=0.1)) +
  xlab("# trees") +
  ylab("R*") +
  theme(text = element_text(size=16, colour="black"),
        axis.text = element_text(colour="black"),
        legend.position = c(0.7, 0.25)) +
  scale_y_continuous(limits=c(0.95, 2.8)) +
  geom_hline(yintercept = 1, linetype=2) +
  scale_color_brewer("Int. depth", palette = "Dark2") +
  guides(colour = guide_legend(nrow = 2, byrow = T)) +
  scale_shape(guide="none") +
  ggtitle("A. GBM")
```

>>>>

Note that the results used in this file were generated using various shell scripts: s_jobScheduler_hypers.sh (for the GBM classifier) and s_jobScheduler_hypers_rf.sh (for the RF classifier)

@@

# GBM
AR1 model
```{r}
g1 <- readRDS("../data/hypers_ar1.rds")$r_star %>% 
  melt(id.vars=c("int.depth", "n.trees")) %>% 
  group_by(int.depth, n.trees) %>% 
  summarise(lower=quantile(value, 0.25),
            middle=quantile(value, 0.5),
            upper=quantile(value, 0.75)) %>% 
  mutate(default=if_else(int.depth==3&n.trees==50, 1, 0)) %>% 
  ggplot(aes(x=as.factor(n.trees), y=middle, colour=as.factor(int.depth), group=as.factor(int.depth))) +
  geom_pointrange(aes(ymin=lower, ymax=upper, shape=as.factor(default)),
                  position=position_dodge2(width=0.1)) +
  geom_line(position=position_dodge2(width=0.1)) +
  xlab("# trees") +
  ylab("R*") +
  theme(text = element_text(size=16, colour="black"),
        axis.text = element_text(colour="black"),
        legend.position = c(0.7, 0.25)) +
  scale_y_continuous(limits=c(0.95, 1.3)) +
  geom_hline(yintercept = 1, linetype=2) +
  scale_color_brewer("Int. depth", palette = "Dark2") +
  guides(colour = guide_legend(nrow = 2, byrow = T)) +
  scale_shape(guide="none") +
  ggtitle("A. GBM")
```

8 schools
```{r}
g1a <- readRDS("../data/hypers_8_schools.rds")$r_star %>% 
  melt(id.vars=c("int.depth", "n.trees")) %>% 
  group_by(int.depth, n.trees) %>% 
  summarise(lower=quantile(value, 0.25),
            middle=quantile(value, 0.5),
            upper=quantile(value, 0.75)) %>% 
  mutate(default=if_else(int.depth==3&n.trees==50, 1, 0)) %>% 
  ggplot(aes(x=as.factor(n.trees), y=middle, colour=as.factor(int.depth), group=as.factor(int.depth))) +
  geom_pointrange(aes(ymin=lower, ymax=upper, shape=as.factor(default)),
                  position=position_dodge2(width=0.1)) +
  geom_line(position=position_dodge2(width=0.1)) +
  xlab("# trees") +
  ylab("R*") +
  theme(text = element_text(size=16, colour="black"),
        axis.text = element_text(colour="black"),
        legend.position = c(0.7, 0.7)) +
  scale_y_continuous(limits=c(0.95, 1.6)) +
  geom_hline(yintercept = 1, linetype=2) +
  scale_color_brewer("Int. depth", palette = "Dark2") +
  guides(colour = guide_legend(nrow = 2, byrow = T)) +
  scale_shape(guide="none") +
  ggtitle("A. GBM")
```

Cauchy
```{r}
g1b <- readRDS("../data/hypers_cauchy.rds")$r_star %>% 
  melt(id.vars=c("int.depth", "n.trees")) %>% 
  group_by(int.depth, n.trees) %>% 
  summarise(lower=quantile(value, 0.25),
            middle=quantile(value, 0.5),
            upper=quantile(value, 0.75)) %>% 
  mutate(default=if_else(int.depth==3&n.trees==50, 1, 0)) %>% 
  ggplot(aes(x=as.factor(n.trees), y=middle, colour=as.factor(int.depth), group=as.factor(int.depth))) +
  geom_pointrange(aes(ymin=lower, ymax=upper, shape=as.factor(default)),
                  position=position_dodge2(width=0.1)) +
  geom_line(position=position_dodge2(width=0.1)) +
  xlab("# trees") +
  ylab("R*") +
  theme(text = element_text(size=16, colour="black"),
        axis.text = element_text(colour="black"),
        legend.position = c(0.7, 0.25)) +
  scale_y_continuous(limits=c(0.95, 2.8)) +
  geom_hline(yintercept = 1, linetype=2) +
  scale_color_brewer("Int. depth", palette = "Dark2") +
  guides(colour = guide_legend(nrow = 2, byrow = T)) +
  scale_shape(guide="none") +
  ggtitle("A. GBM")
```

### 2020-11-09 src/s_ml.Rmd
cleaning up repo and rerunning rhat experiments

@@

Function to fit any ML model in Caret
```{r}
r_star_ml_variety <- function(x, method_, caretGrid){

  split_chains=T
  training_percent=0.7
  if(split_chains)
    x <- split_data(x)
  nparams <- dim(x)[3]
  nchains <- dim(x)[2]
  niter <- dim(x)[1]
  m_flattened <- matrix(nrow = nrow(x) * nchains,
                        ncol = (nparams + 1))
  k <- 1
  for(i in 1:nchains){
    for(j in 1:nrow(x)){
      m_flattened[k, 1:nparams] <- x[j, i, ]
      m_flattened[k, (nparams + 1)] <- i
      k <- k + 1
    }
  }
  m_flattened <- m_flattened %>% 
    as.data.frame()
  colnames(m_flattened)[nparams + 1] <- "chain"
  r <- m_flattened %>% 
    mutate(chain=as.factor(chain))
  # if only 1 param, add in a column of random noise since gbm requires >1 dims
  if(nparams==1)
    r <- r %>% 
      mutate(V_new=rnorm(nrow(r)))

  rand_samples <- sample(1:nrow(r), training_percent * nrow(r))
  training_data <- r[rand_samples, ]
  testing_data <- r[-rand_samples, ]

  if(method_!="multinom")
      gbmFit <- train(chain ~ ., data = training_data, 
                   trControl = trainControl(method = 'none'),
                   method=method_,
                   tuneGrid = caretGrid)
  else
    gbmFit <- train(chain ~ ., data = training_data, 
                 trControl = trainControl(method = 'none'),
                 method=method_,
                 tuneGrid = caretGrid,
                 MaxNWts=10000
                 )
  plda <- predict(object=gbmFit, newdata=testing_data)
  a_accuracy <- 
    tibble(predicted=plda, actual=testing_data$chain) %>%
    mutate(correct=if_else(predicted==actual, 1, 0)) %>% 
    summarise(mean(correct)) %>% 
    pull()
  return(a_accuracy * n_distinct(training_data$chain))
}

f_replicate_gridded <- function(x, method_, caretGrids_){
  r_stars <- vector(length = nrow(caretGrids_))
  times <- vector(length = nrow(caretGrids_))
  for(i in 1:nrow(caretGrids_)){
    start.time <- Sys.time()
    r_stars[i] <- r_star_ml_variety(x, method_, caretGrids_[i, ])
    end.time <- Sys.time()
    times[i] <- end.time - start.time
  }
  return(list(r_star=r_stars, time=times))
}

f_run_all <- function(methods, list_of_caret_grids, f_data_generator){
  x <- f_data_generator()
  r_stars <- vector(length = length(methods))
  times <- vector(length = length(methods))
  hypers <- vector(length = length(methods), mode="list")
  for(i in seq_along(r_stars)){
    print(methods[i])
    a_grid <- list_of_caret_grids[[i]]
    a <- f_replicate_gridded(x, methods[i], a_grid)
    r_stars[i] <- max(a$r_star)
    a_ind <- which.max(a$r_star)
    times[i] <- a$time[a_ind]
    hypers[[i]] <- a_grid[a_ind, ]
  }
  return(tibble(r_star=r_stars, method=methods, time=times, hyper=hypers))
}

f_run_all_replicates <- function(niterations, methods, list_of_caret_grids, f_data_generator){
  for(i in 1:niterations){
    print(i)
    temp_df <- f_run_all(methods, list_of_caret_grids, f_data_generator) %>% mutate(iter=i)
    if(i==1)
      big_df <- temp_df
    else
      big_df <- big_df %>% bind_rows(temp_df)
  }
  return(big_df)
}

tunegrid_gbm <- expand.grid(interaction.depth=1, 
                             n.trees = c(400),
                             shrinkage=c(0.1),
                             n.minobsinnode=c(1))
tunegrid_rf <- tibble(mtry = c(1, 5, 15))
tunegrid_knn <- tibble(k = c(5, 10, 15, 20, 40))
tunegrid_svm <- tibble(C = c(0.25, 0.5, 0.75))
tunegrid_multinom <- tibble(decay=c(0.1, 0.2, 0.5, 1))
tunegrid_xgbtree <- expand_grid(nrounds = c(1, 10),
                       max_depth = c(1, 4),
                       eta = c(.1, .4),
                       gamma = 0,
                       colsample_bytree = .7,
                       min_child_weight = 1,
                       subsample = c(.8, 1))
```

# AR1
```{r}
f_ar1 <- function(rho, sigma, L){
  x <- vector(length = L)
  x[1] <- rnorm(1, 0, sd=sigma)
  for(i in 2:L)
    x[i] = rho * x[i - 1] + rnorm(1, 0, sd=sigma)
  return(x)
}

# Generates three chains with same var; one with a different var
f_generate_lower_var_four <- function(var_ratio, rho, sigma, L){
  x <- matrix(nrow = L, ncol = 4)
  for(i in 1:3)
    x[, i] <- f_ar1(rho, sigma, L)
  z <- f_ar1(rho, sigma * sqrt(var_ratio), L)
  x[, 4] <- z
  return(x)
}

f_data_ar1 <- function(){
  temp <- f_generate_lower_var_four(1/3, 0.3, 1, 1000)
  a_array <- array(dim=c(1000, 4, 1))
  a_array[,,1] <- temp
  return(a_array)
}

# temp_df <- f_run_all_replicates(2, c("gbm", "rf", "knn", "svmLinear", "multinom"),
#           list(tunegrid_gbm, tunegrid_rf, tunegrid_knn, tunegrid_svm, tunegrid_multinom),
#           f_data_ar1)

orders <- c("rf", "xgbTree", "gbm", "knn", "multinom", "svmLinear")
lookup <- tibble(method=orders,
                 new=c("RF", "xgbTree", "GBM", "KNN", "GLM", "SVM"))

@@

# 8 schools
```{r}
source("eight_schools.data.R")
eight_schools <- list(J=J, y=y, sigma=sigma)
model_cp <- stan_model("eight_schools_cp.stan")
model_ncp <- stan_model("eight_schools_ncp.stan")

f_data_8_schools <- function(){
  fit_ncp <- sampling(
    model_ncp, data = eight_schools,
    iter = 2000, chains = 4, refresh = 0,
    control = list(adapt_delta = 0.95)
    )
  x_ncp <- rstan::extract(fit_ncp, permuted=F)
}

# temp_df <- f_run_all_replicates(2, c("gbm", "rf", "knn", "svmLinear", "multinom"),
#           list(tunegrid_gbm, tunegrid_rf, tunegrid_knn, tunegrid_svm, tunegrid_multinom),
#           f_data_8_schools)

temp_df1 <- readRDS("../data/ml_comp_hypers_set_8_schools.rds")  %>% 
  filter(method!="xgbTree") %>%
  select(method, iter, r_star, time) %>% 
  left_join(lookup, by="method") %>% 
  select(-method) %>% 
  rename(method=new) %>% 
  mutate(method=as.factor(method)) %>% 
  mutate(method=fct_relevel(method, lookup$new)) %>% 
  rename(`R*`=r_star, `Time`=time) %>% 
  melt(id.vars=c("method", "iter")) %>% 
  group_by(method, variable) %>% 
  summarise(lower=quantile(value, 0.25),
            middle=quantile(value, 0.5),
            upper=quantile(value, 0.75)) %>% 
  mutate(model="D. 8 schools")
```

# Cauchy
```{r}
f_data_cauchy <- function(){
  fit_nom <- stan(file = 'cauchy_alt_1.stan',
                refresh = 0)
  x <- rstan::extract(fit_nom, permuted=F)
  return(x)
}

# temp_df <- f_run_all_replicates(2, c("gbm", "rf", "knn", "svmLinear", "multinom"),
#           list(tunegrid_gbm, tunegrid_rf, tunegrid_knn, tunegrid_svm, tunegrid_multinom),
#           f_data_cauchy)
temp_df2 <- readRDS("../data/ml_comp_hypers_set_cauchy.rds") %>% 
  filter(method!="xgbTree") %>%
  select(method, iter, r_star, time) %>% 
  left_join(lookup, by="method") %>% 
  select(-method) %>% 
  rename(method=new) %>% 
  mutate(method=as.factor(method)) %>% 
  mutate(method=fct_relevel(method, lookup$new)) %>% 
  rename(`R*`=r_star, `Time`=time) %>% 
  melt(id.vars=c("method", "iter")) %>% 
  group_by(method, variable) %>% 
  summarise(lower=quantile(value, 0.25),
            middle=quantile(value, 0.5),
            upper=quantile(value, 0.75)) %>% 
  mutate(model="C. Cauchy")
```

# Multivariate normal
```{r}
f_data_normal <- function(){
  N <- 250
  A <- rWishart(1, 250, diag(N))[,,1]
  model <- stan_model("mvt_250_ncp.stan")
  fit <- sampling(model, data=list(N=N, A=A), iter=1000, chains=4)
  x <- rstan::extract(fit, permuted=F)
  return(x)
}

# temp_df <- f_replicate_gridded(x, "rf", tunegrid_rf)

temp_df3 <- readRDS("../data/ml_comp_hypers_set_normal_250.rds") %>% 
  filter(method!="xgbTree") %>%
  select(method, iter, r_star, time) %>% 
  left_join(lookup, by="method") %>% 
  select(-method) %>% 
  rename(method=new) %>% 
  mutate(method=as.factor(method)) %>% 
  mutate(method=fct_relevel(method, lookup$new)) %>% 
  rename(`R*`=r_star, `Time`=time) %>% 
  melt(id.vars=c("method", "iter")) %>% 
  group_by(method, variable) %>% 
  summarise(lower=quantile(value, 0.25),
            middle=quantile(value, 0.5),
            upper=quantile(value, 0.75)) %>% 
  mutate(model="B. 250D normal")

@@

# Check for false positives with random forests
```{r}
f_data_converged <- function(){
  d <- 10
  n <- 2000
  nchain <- 4

  x <- rnorm(d * n * nchain)
  x <- array(x, dim=c(n, nchain, d))
  return(x)
}

temp_df <- f_run_all_replicates(10, c("gbm", "rf"),
          list(tunegrid_gbm, tunegrid_rf),
          f_data_converged)
temp_df %>% 
  ggplot(aes(x=as.factor(method), y=r_star)) +
  geom_boxplot()
```

# Setting hyperparameters for random forest:
"Influence of Hyperparameters on Random Forest Accuracy"
Simon Bernard, Laurent Heutte, Sebastien Adam, 2009
Use mtry=sqrt(number features)

whereas for gbms / xgboost, performance depends on lots of things

>>>>

Note that, to generate the results in this section, we used the shell file 
s_jobScheduler_ml_hypers_set.sh

@@

# AR1
```{r}
orders <- c("rf", "xgbTree", "gbm", "knn", "multinom", "svmLinear")
lookup <- tibble(method=orders,
                 new=c("RF", "xgbTree", "GBM", "KNN", "GLM", "SVM"))

@@

# 8 schools
```{r}
temp_df1 <- readRDS("../data/ml_comp_hypers_set_8_schools.rds")  %>% 
  filter(method!="xgbTree") %>%
  select(method, iter, r_star, time) %>% 
  left_join(lookup, by="method") %>% 
  select(-method) %>% 
  rename(method=new) %>% 
  mutate(method=as.factor(method)) %>% 
  mutate(method=fct_relevel(method, lookup$new)) %>% 
  rename(`R*`=r_star, `Time`=time) %>% 
  melt(id.vars=c("method", "iter")) %>% 
  group_by(method, variable) %>% 
  summarise(lower=quantile(value, 0.25),
            middle=quantile(value, 0.5),
            upper=quantile(value, 0.75)) %>% 
  mutate(model="D. 8 schools")
```

# Cauchy
```{r}
temp_df2 <- readRDS("../data/ml_comp_hypers_set_cauchy.rds") %>% 
  filter(method!="xgbTree") %>%
  select(method, iter, r_star, time) %>% 
  left_join(lookup, by="method") %>% 
  select(-method) %>% 
  rename(method=new) %>% 
  mutate(method=as.factor(method)) %>% 
  mutate(method=fct_relevel(method, lookup$new)) %>% 
  rename(`R*`=r_star, `Time`=time) %>% 
  melt(id.vars=c("method", "iter")) %>% 
  group_by(method, variable) %>% 
  summarise(lower=quantile(value, 0.25),
            middle=quantile(value, 0.5),
            upper=quantile(value, 0.75)) %>% 
  mutate(model="C. Cauchy")
```

# Multivariate normal
```{r}
temp_df3 <- readRDS("../data/ml_comp_hypers_set_normal_250.rds") %>% 
  filter(method!="xgbTree") %>%
  select(method, iter, r_star, time) %>% 
  left_join(lookup, by="method") %>% 
  select(-method) %>% 
  rename(method=new) %>% 
  mutate(method=as.factor(method)) %>% 
  mutate(method=fct_relevel(method, lookup$new)) %>% 
  rename(`R*`=r_star, `Time`=time) %>% 
  melt(id.vars=c("method", "iter")) %>% 
  group_by(method, variable) %>% 
  summarise(lower=quantile(value, 0.25),
            middle=quantile(value, 0.5),
            upper=quantile(value, 0.75)) %>% 
  mutate(model="B. 250D normal")

@@

### 2020-11-09 src/s_mvt_normal.Rmd
cleaning up repo and rerunning rhat experiments

# Collect Rhat
full_data <- rstan::extract(fit, permuted=F)
a_sum <- monitor_extra(full_data)
rhat <- a_sum$zfsRhat
rhat1 <- a_sum$zsRhat
rhat <- tibble(rhat, rhat1) %>% 
  apply(1, max)

>>>>

# Collect Rhat and calculate as in posterior package
full_data <- rstan::extract(fit, permuted=F)
a_sum <- monitor_extra(full_data)
rhat <- a_sum$zfsRhat
rhat1 <- a_sum$zsRhat
rhat <- tibble(rhat, rhat1) %>% 
  apply(1, max)

### 2020-11-09 src/s_ovarian_prostate.Rmd
cleaning up repo and rerunning rhat experiments

mon <- monitor_extra(split_data(x))
saveRDS(mon, "../data/ovarian_long_mon.rds")
full_data <- rstan::extract(fit, permuted=F)
r_star <- r_star_dist(full_data)
saveRDS(r_star, "../data/ovarian_long_r_star.rds")
```

@@

x <- rstan::extract(fit, permuted=F)
mon <- monitor_extra(split_data(x))
saveRDS(mon, "../data/ovarian_short_mon.rds")
full_data <- rstan::extract(fit, permuted=F)
r_star <- r_star_dist(full_data)
saveRDS(r_star, "../data/ovarian_short_r_star.rds")
```

@@

g <- tibble(long=r_star_longer, short=r_star_shorter, metric="A. R*") %>% 
  bind_rows(tibble(long=mon_longer$zsRhat, short=mon_shorter$zsRhat, metric="B. Split-Rhat")) %>% 
  bind_rows(tibble(long=mon_longer$zsseff, short=mon_shorter$zsseff, metric="C. Bulk-ESS")) %>% 
  bind_rows(tibble(long=mon_longer$tailseff, short=mon_shorter$tailseff, metric="D. Tail-ESS")) %>% 
  melt(id.vars="metric") %>% 
  mutate(metric=fct_relevel(as.factor(metric), "A. R*", "B. Split-Rhat", "C. Bulk-ESS", "D. Tail-ESS")) %>% 
  ggplot(aes(x=value, fill=as.factor(variable))) +
  geom_histogram(position="identity", alpha=0.6) +
  facet_wrap(~metric, scales="free") +
  scale_fill_grey("MCMC detail", labels=c("4 chains: long", "16 chains: short")) +
  theme(strip.text.x = element_text(size = 20, colour="black"),
        text = element_text(size=18, colour="black"),
        axis.text = element_text(size=18, colour="black"),
        legend.text = element_text(size=18, colour="black"),
        axis.title = element_text(size=18, colour="black"),
        axis.title.x = element_blank(),
        legend.position = "top") +
  ylab("Count")
ggsave("../output/ovarian.pdf", g, width = 12, height = 8)
```

@@

mon <- monitor_extra(split_data(x))
saveRDS(mon, "../data/prostate_long_mon.rds")
full_data <- rstan::extract(fit, permuted=F)

# Thin data again
r_star <- r_star_dist(full_data[, , seq(1, 18106, 5)])
saveRDS(r_star, "../data/prostate_long_r_star.rds")
```

@@

x <- rstan::extract(fit, permuted=F)
mon <- monitor_extra(split_data(x))
saveRDS(mon, "../data/prostate_short_mon.rds")
full_data <- rstan::extract(fit, permuted=F)
r_star <- r_star_dist(full_data[, , seq(1, 18106, 5)])
saveRDS(r_star, "../data/prostate_short_r_star.rds")
```

@@

g <- tibble(long=r_star_longer, short=r_star_shorter, metric="A. R*") %>% 
  bind_rows(tibble(long=mon_longer$zsRhat, short=mon_shorter$zsRhat, metric="B. Split-Rhat")) %>% 
  bind_rows(tibble(long=mon_longer$zsseff, short=mon_shorter$zsseff, metric="C. Bulk-ESS")) %>% 
  bind_rows(tibble(long=mon_longer$tailseff, short=mon_shorter$tailseff, metric="D. Tail-ESS")) %>% 
  melt(id.vars="metric") %>% 
  mutate(metric=fct_relevel(as.factor(metric), "A. R*", "B. Split-Rhat", "C. Bulk-ESS", "D. Tail-ESS")) %>% 
  ggplot(aes(x=value, fill=as.factor(variable))) +
  geom_histogram(position="identity", alpha=0.6) +
  facet_wrap(~metric, scales="free") +
  scale_fill_grey("MCMC detail", labels=c("4 chains: long", "16 chains: short")) +
  theme(strip.text.x = element_text(size = 20, colour="black"),
        text = element_text(size=18, colour="black"),
        axis.text = element_text(size=18, colour="black"),
        legend.text = element_text(size=18, colour="black"),
        axis.title = element_text(size=18, colour="black"),
        axis.title.x = element_blank(),
        legend.position = "top") +
  ylab("Count") +
  scale_x_continuous(limits=my_breaks)
ggsave("../output/prostate.pdf", g, width = 12, height = 8)
```

>>>>

mon <- monitor_extra(x)
saveRDS(mon, "../data/ovarian_long_mon.rds")
full_data <- rstan::extract(fit, permuted=F)
r_star <- r_star(full_data, method = "gbm", uncertainty = T)
saveRDS(r_star, "../data/ovarian_long_r_star.rds")
```

@@

x <- rstan::extract(fit, permuted=F)
mon <- monitor_extra(x)
saveRDS(mon, "../data/ovarian_short_mon.rds")
full_data <- rstan::extract(fit, permuted=F)
r_star <- r_star(full_data, method = "gbm", uncertainty = T)
saveRDS(r_star, "../data/ovarian_short_r_star.rds")
```

@@

# find max of rank normalized split-Rhat and rank normalized folded-split-Rhat
f_rhat_max <- function(mon) {
  rhat <- mon$zsRhat
  rhat1 <- mon$zfsRhat
  rhat <- tibble(rhat, rhat1) %>% 
    apply(1, max)
  return(rhat)
}

g <- tibble(long=r_star_longer, short=r_star_shorter, metric="A. R*") %>% 
  bind_rows(tibble(long=f_rhat_max(mon_longer), short=f_rhat_max(mon_shorter), metric="B. Split-Rhat"))%>% 
  bind_rows(tibble(long=mon_longer$zsseff, short=mon_shorter$zsseff, metric="C. Bulk-ESS")) %>% 
  bind_rows(tibble(long=mon_longer$tailseff, short=mon_shorter$tailseff, metric="D. Tail-ESS")) %>% 
  melt(id.vars="metric") %>% 
  mutate(metric=fct_relevel(as.factor(metric), "A. R*", "B. Split-Rhat", "C. Bulk-ESS", "D. Tail-ESS")) %>% 
  ggplot(aes(x=value, fill=as.factor(variable))) +
  geom_histogram(position="identity", alpha=0.6) +
  facet_wrap(~metric, scales="free") +
  scale_fill_grey("MCMC detail", labels=c("4 chains: long", "16 chains: short")) +
  theme(strip.text.x = element_text(size = 20, colour="black"),
        text = element_text(size=18, colour="black"),
        axis.text = element_text(size=18, colour="black"),
        legend.text = element_text(size=18, colour="black"),
        axis.title = element_text(size=18, colour="black"),
        axis.title.x = element_blank(),
        legend.position = "top") +
  ylab("Count")
ggsave("../output/ovarian.pdf", g, width = 12, height = 8)
```

@@

mon <- monitor_extra(x)
saveRDS(mon, "../data/prostate_long_mon.rds")
full_data <- rstan::extract(fit, permuted=F)

# Thin data again
r_star <- r_star(full_data[, , seq(1, 18106, 5)], method = "gbm", uncertainty = T)
saveRDS(r_star, "../data/prostate_long_r_star.rds")
```

@@

x <- rstan::extract(fit, permuted=F)
mon <- monitor_extra(x)
saveRDS(mon, "../data/prostate_short_mon.rds")
full_data <- rstan::extract(fit, permuted=F)
r_star <- r_star(full_data[, , seq(1, 18106, 5)], method = "gbm", uncertainty = T)
saveRDS(r_star, "../data/prostate_short_r_star.rds")
```

@@

g <- tibble(long=r_star_longer, short=r_star_shorter, metric="A. R*") %>% 
  bind_rows(tibble(long=f_rhat_max(mon_longer), short=f_rhat_max(mon_shorter), metric="B. Split-Rhat")) %>% 
  bind_rows(tibble(long=mon_longer$zsseff, short=mon_shorter$zsseff, metric="C. Bulk-ESS")) %>% 
  bind_rows(tibble(long=mon_longer$tailseff, short=mon_shorter$tailseff, metric="D. Tail-ESS")) %>% 
  melt(id.vars="metric") %>% 
  mutate(metric=fct_relevel(as.factor(metric), "A. R*", "B. Split-Rhat", "C. Bulk-ESS", "D. Tail-ESS")) %>% 
  ggplot(aes(x=value, fill=as.factor(variable))) +
  geom_histogram(position="identity", alpha=0.6) +
  facet_wrap(~metric, scales="free") +
  scale_fill_grey("MCMC detail", labels=c("4 chains: long", "16 chains: short")) +
  theme(strip.text.x = element_text(size = 20, colour="black"),
        text = element_text(size=18, colour="black"),
        axis.text = element_text(size=18, colour="black"),
        legend.text = element_text(size=18, colour="black"),
        axis.title = element_text(size=18, colour="black"),
        axis.title.x = element_blank(),
        legend.position = "top") +
  ylab("Count") +
  scale_x_continuous(limits=my_breaks)
ggsave("../output/prostate.pdf", g, width = 12, height = 8)
```
